\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{lmodern}
\usepackage[hyphens]{url}
%\usepackage{kpfonts}
\usepackage{fourier}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\title{EMNLP 2018 Childcare policy}
%\author{Swapna Somasundaran}

\begin{document}
\maketitle

\section*{Purpose} 
ACL instituted family-friendly policies in recent years, which has been greatly appreciated. 
 The current childcare support provides on-site daycare to participants attending the conference at a subsidized rate. However, this can become cost-prohibitive if the enrollment is low. 
  In order to address this issue, and to widen the scope of childcare help, we are introducing a reimbursement model at EMNLP 2018.  
%The current 
%The current childcare support model, which is in the form of subsidized onsite daycare, has been cost-prohibitive. This is especially so when the number of participants are few.  Hence this u 
%Childcare has mainly been in the form of onsite childcare provided at subsidized rates.  it has proven to be cost-prohibitive. 

\section*{Scope}
This childcare policy applies to EMNLP 2018 attendees applying for grants to cover childcare costs on account of their conference travel. 


\section*{Definitions}


\section*{Policy}

Grants of upto \$??  per family are available for EMNLP 2018 attendees who are bringing small children to the conference or who incur extra expenses in leaving their children at home. 
The grants will be given as a reimbursement for expenses, however, attendees are responsible for making their own arrangements for child care. If requests exceed available funding, or if additional funding becomes available, preference will be given to students,  recent graduates or those in early stages of their careers,  who are presenting at the conference.

\subsection*{Reimbursable Expenses}
 A signed statement by caregiver including the total amount paid per day is required. Provider must submit his/her tax id number. 
\begin{itemize}
\item Child care expenses at the site of the meeting
\item    Extra child/dependent care expenses at home incurred because the primary caregiver was attending the meeting (such as overtime at a child care center, cost of a sitter, etc.)
\item Travel of a relative or other care provider to your home to care for your child while attending the conference. \nocite{ASCBWomenCell} %http://stemfamilytravel.org/2015%20ASCB.html
\item Travel of your child(ren) to the location of a care provider who does not live in your community. \nocite{ASCBWomenCell} %http://stemfamilytravel.org/2015%20ASCB.html 
\end{itemize}

\subsection*{\textit{Not} Reimbursable Expenses}


\begin{itemize}
    \item         Regular/Ongoing home-based child/dependent care expenses
 \item   Travel or other expenses related to the attendee's participation in the meeting (including meeting registration, meals, travel to the meeting, or other expenses the attendee would already be incurring by attending the meeting)
\item    Meals for the child
\item    Tickets to local museums, amusement parks, etc. 
\item    Expenses incurred in bringing a caregiver and/or dependent to the conference \footnote{This is covered in a few venues}  %TODO this is usually covered in other conferences. 
\item Travel expenses for the child


\end{itemize}

\section*{Procedures}
\begin{itemize}


\item Recipients of a childcare grant must submit receipts for reimbursable expenses (for example, an invoice submitted by the child care provider)
\item Reimbursements will be distributed after the conference, after receipt of documentation.
\item Reimbursement forms will be available online (????)
\item All documentation should be submitted to Priscilla 
\item (????) All applicable federal and state taxes will be collected at a rate of 28\%, however, the grant monies will be grossed-up to allow for these taxes
 
 \end{itemize}

\section*{Deadlines}

Application Deadline:  \\
Notification of acceptance: \\
Documentation Submission deadline:  \\
Reimbursement window: \\


\pagebreak
\section{Appendix A}
\nocite{STEMTravelgrant}

Listed below are the childcare reimbursements for other scientific societies. \\

\begin{tabular}{|c|c|} \hline
 Organization &  Amount offered in USD, per family \\ \hline
  American Astronomical Society\cite{AmericanAstronomicalSociety} & 250  \\ \hline
   American Physical Society \cite{AmericanPhysicalSociety} & 400 \\ \hline
   IEEE International Conference on Communications\cite{IEEEInternationalConference} & 400 \\ \hline
   AMS and the MAA (2016)\cite{AmericanMathematicalSociety}  & 250 \\ \hline
   Materials Research Society\cite{MaterialsResearchSociety} & 300 \\ \hline
   Society for Industrial and Applied Mathematics (SIAM)\cite{SocietyIndustrialApplied} & 250 \\ \hline 
   
\end{tabular}



\bibliographystyle{plain}
\bibliography{/Users/ssomasundaran/GoogleDriveNoSpace/bib2013/childcare}
\end{document}